\huge{\textbf{Gesture Based UI Development}} \\ \LARGE{Research Paper}

### 2021-02-14 paper/main.tex
Paper is complete but will need some further editing.

\subsection{How are gestures used in everyday life for communication with others?}
\subsection{How are gestures defined and become accepted to represent various aspects of
communication?}

@@

@@

\section{Conclusions}
% Conclusions are what you have learned from your research. This is your reflection on the current state of the art and the possible future directions of gesture-based user interfaces.

@@

>>>>

Gestures have become a part of everyday Communication. People do it naturally without thinking. Gestures go hand and hand with talking. They allow people to express themselves further. "Communication is the act of conveying meanings from one entity or group to another through the use of mutually understood signs, symbols, and semiotic rules. The main steps inherent to all Communication are: The formation of communicative motivation or reason." \cite{ref14}
Gestures do have their advantages and disadvantages. One major disadvantage is language barriers. For example, a gesture could mean something in one language and then mean something entirely different in another. One gesture that can bring some confusion is the 'Okay' gesture. In most English-speaking countries, this means okay, whereas, in Japan, it means Money, and sometimes the gesture is made with the three fingers at the bottom. In Brazil, it is a rude gesture. In the Arab world, this sign's shaking represents the evil eye and is used as a curse or a threat, sometimes combined with verbal condemnation. The 'Come here' gesture, usually done by the index finger, is used quite a lot in English speaking countries. In the Philippines, it is only used for dogs as it is believed to be derogatory to use on people, and people could get arrested for using it. Just from these two gestures, it is shown that how different they can be when they look the same and can cause miscommunication.
\cite{ref15}

@@

In Applications, Gestures are the new clicks. These gestures obtain a close personal connection with the content and improve the direct manipulation of on-screen objects. Designers have to be careful with applications as gestures can vary in what they mean and, unfortunately, limit the number of gestures in an application. However, this issue is not necessarily bad as the gesture will be more remember-able for users as there are only a few implemented. As users are accustomed to everyday gestures and do not like being challenged to learn many ways to do the same thing, this is a complex design environment. A pleasant aspect of the experience could be custom gestures in games and other immersive applications. It is easier to use familiar gestures in other apps because additional effort is not needed to discover or remember them.
\cite{ref16}

@@

Many smartphones rely on taps and swipes. They comes very naturally to most people. These taps can be more than one to perform different functions. "In general, having a single action available on swipe-right that starts or progresses the most important task is recommended, and - optionally - a single action is made available on left swipe."
\cite{ref17}
For the implementation of these navigation tools developers had to take take many things into account such as what does one tap, two taps, or a swipe do? The navigation bar that is usually on Android phones has three inter-grated buttons. The functions of these buttons can be customized. Their standard functionalities are to go back, to view the app menu, and to see already opened apps. IOS devices do the same thing but with a single button and swipes. The Android navigation bar can be hard to use initially, but there is more control from these three buttons than the IOS setup. These are two similar devices intended to do the same thing, and they both do them differently.

\section{Conclusion}
% Conclusions are what you have learned from your research. This is your reflection on the current state of the art and the possible future directions of gesture-based user interfaces.

Throughout this paper, User Experience Evolution, Gestures as a Communication Tool, Challenges for the Design of Gesture Applications, and the Challenges for Implementation of Gestures were all discussed. By doing this research paper, I learned that the user interface has a long and exciting history. It was enjoyable to learn where the devices that are around us today originated. Gesture Based technology is a fascinating area of the modern world, and doing this paper, has inspired me to always keep an eye out for these devices and be up to date and their current status.
It is exciting to think about where these technologies might be in the future and how advanced they will be. Above everything else, I wholeheartedly believe machine learning will help these technologies become better with time and hard work from humans and machines.

@@

\bibitem{ref14} Wikipedia - Communication
\newline
URL: \url{https://g.co/kgs/2N6sjN}

\bibitem{ref15} Bright Side - 15 Hand Gestures That Have Different Meanings Overseas
\newline
URL: \url{https://tinyurl.com/yxl6kcw9}

\bibitem{ref16} Apple Developer - Gestures
\newline
URL: \url{https://tinyurl.com/y9zkjmpa}

\bibitem{ref17} Microsoft Docs - Implementation Tips for Gestures
\newline
URL: \url{https://tinyurl.com/y2p5trby}
